The Impact of ChatGPT news on MSFT

### 2023-12-02 MSFT.Rmd
included some plots

First we get the MSFT price data via yahoo API and we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.

```{r echo=FALSE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)

@@

MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-11-18", periodicity = "daily", auto.assign=FALSE)[,6]

adf.test(MSFT) 
```

@@

```{r pressure, echo=FALSE}
MSFT_returns <- na.omit(diff(log(MSFT)))
adf.test(MSFT_returns)
```
Now, that we deal with stationary data we can begin with our analysis.

@@

```{r pressure, echo=FALSE}
coeftest(VAR_est)
MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

@@

```{r pressure, echo=FALSE}

causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
causality(VAR_est, cause="Inflation_CH")["Granger"]

@@

```{r pressure, echo=FALSE}

plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))

>>>>

First we get the recent MSFT price data from the beginning of 2022 up to today via yahoo API and plot it so that we can inspect if the time series already behaves stationary

```{r echo=FALSE, include=TRUE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)

@@

MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]

ChatGPT <- read.csv("ChatGPT.csv")

plot(MSFT)
```
We see a clear trend, which is an indicator for non-stationarity, so we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.

```{r echo=FALSE, include=TRUE}
adf.test(MSFT) 
```

@@

```{r echo=FALSE, include=TRUE}
MSFT_returns <- na.omit(diff(log(MSFT)))
adf.test(MSFT_returns)

plot(MSFT_returns)
```
Now, that we deal with stationary data we can begin with our analysis.

@@

```{r echo=FALSE, include=TRUE}
coeftest(VAR_est)
MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

@@

```{r echo=FALSE, include=TRUE}
causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
causality(VAR_est, cause="Inflation_CH")["Granger"]

@@

```{r echo=FALSE, include=TRUE}
plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))
